Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2017-04-27 Draft_2.tex
Added list of figures and tables, also added problem definition subsection, as per Dimitar's request

        \Large
        Wordcount - 11799\\
        \small
        (Wordcount produced using wc - w, \\
        this includes all the body of the report,\\
         and Appendix A)\\
        \large
        \vspace{0.8cm}
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        25 April 2017

@@

\tableofcontents

@@

@@

\newpage
\appendix
\section*{Appendix A}
\label{sec:AppA}
\begin{lstlisting}[caption={A trace of the STM throughout runtime}, captionpos=b, label={lst:STMTrace}]

==========================================
---------------------------------
Synset('jury.n.01') - 2.2015449935
Synset('jury.n.02') - 2.2015449935
Synset('execution.n.06') - 0.400514997832
Synset('implementation.n.02') - 0.400514997832
Synset('police.n.01') - 0.400514997832
---------------------------------
---------------------------------
Synset('state.v.01') - 1.79514049042
Synset('allege.v.01') - 1.7015449935
Synset('suppose.v.01') - 1.7015449935
Synset('read.v.02') - 1.7015449935
Synset('claim.v.04') - 1.40051499783
---------------------------------

Implementation Georgia automobile title law recommended jury 
==========================================
---------------------------------
Synset('execution.n.06') - 1.90051499783
Synset('implementation.n.02') - 1.90051499783
Synset('law.n.01') - 1.90051499783
Synset('law.n.02') - 1.90051499783
Synset('police.n.01') - 1.90051499783
---------------------------------
---------------------------------
Synset('state.v.01') - 1.3263389894
Synset('allege.v.01') - 1.2015449935
Synset('suppose.v.01') - 1.2015449935
Synset('read.v.02') - 1.2015449935
Synset('take.v.02') - 1.15040647846
---------------------------------

urged Legislature provide funds re-set date implementation law be effected 
==========================================
---------------------------------
Synset('funds.n.01') - 1.90051499783
Synset('fund.n.01') - 1.90051499783
Synset('store.n.02') - 1.90051499783
Synset('investment_company.n.01') - 1.90051499783
Synset('execution.n.06') - 1.40051499783
---------------------------------
---------------------------------
Synset('take.v.01') - 1.90051499783
Synset('take.v.02') - 1.90051499783
Synset('lead.v.01') - 1.90051499783
Synset('take.v.04') - 1.90051499783
Synset('claim.v.04') - 1.90051499783
---------------------------------

grand jury took a swipe at handling funds child welfare services foster homes 
=====================

>>>>

        \Large
        Wordcount - 11798\\
        \small
        (Wordcount produced using wc - w, \\
        this includes all the body of the report,\\
         and Appendix A)\\
        \large
        \vspace{0.8cm}
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        25 April 2017

@@

\tableofcontents
\listoffigures
\listoftables

@@

\subsection{Problem Definition}
\label{sec:IntroProbDef}

@@

\newpage
\appendix
\section*{Appendix A}
\label{sec:AppA}
\begin{lstlisting}[caption={A trace of the STM throughout runtime}, captionpos=b, label={lst:STMTrace}, basicstyle=\small]
---------------------------------
Synset('jury.n.01') - 2.2015449935
Synset('jury.n.02') - 2.2015449935
Synset('execution.n.06') - 0.400514997832
Synset('implementation.n.02') - 0.400514997832
Synset('police.n.01') - 0.400514997832
---------------------------------
Synset('state.v.01') - 1.79514049042
Synset('allege.v.01') - 1.7015449935
Synset('suppose.v.01') - 1.7015449935
Synset('read.v.02') - 1.7015449935
Synset('claim.v.04') - 1.40051499783
---------------------------------
Implementation Georgia automobile title law recommended jury 
==========================================
---------------------------------
Synset('execution.n.06') - 1.90051499783
Synset('implementation.n.02') - 1.90051499783
Synset('law.n.01') - 1.90051499783
Synset('law.n.02') - 1.90051499783
Synset('police.n.01') - 1.90051499783
---------------------------------
Synset('state.v.01') - 1.3263389894
Synset('allege.v.01') - 1.2015449935
Synset('suppose.v.01') - 1.2015449935
Synset('read.v.02') - 1.2015449935
Synset('take.v.02') - 1.15040647846
---------------------------------
urged Legislature provide funds re-set date implementation law be effected 
==========================================
---------------------------------
Synset('funds.n.01') - 1.90051499783
Synset('fund.n.01') - 1.90051499783
Synset('store.n.02') - 1.90051499783
Synset('investment_company.n.01') - 1.90051499783
Synset('execution.n.06') - 1.40051499783
---------------------------------
Synset('take.v.01') - 1.90051499783
Synset('take.v.02') - 1.90051499783
Synset('lead.v.01') - 1.90051499783
Synset('take.v.04') - 1.90051499783
Synset('claim.v.04') - 1.90051499783
---------------------------------
grand jury took a swipe at handling funds child welfare services foster homes 
=====================
